A Bias-Variance Decomposition of Information Transfer in Multi-Task Learning

### 2020-08-17 arxiv/proof_examples.tex
pf

For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
\begin{lemma}[The isotropic model]\label{prop_model_shift_tight}
		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_2$ is a random vector that has i.i.d. entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d. entries with mean $0$, variance $d^2$ and finite moments up to any order. Denote
		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in \eqref{defnpihat}.	Then we have with high probability,
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
		\end{align*}
		where $\Delta_{\vari}$ was defined in \eqref{Deltavarv}.
\end{lemma}

@@

For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d. entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$. Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$, {\cor(start here)}
\begin{align}
&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2],\label{anotherbeta}
\end{align}
where we denoted $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}. Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
\begin{align*}
v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
\end{align*}
Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric} again, we obtain that
\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
where
$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
Note that $\delta^\star_{\bias}(v) \sim p$, hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
\be\label{replaceest}
  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
\ee
Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Theorem \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}. In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term, We omit the details.
\end{proof}

We show that for the isotropic model, the optimum of $\hat v$ is very close to 1.
This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
%Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
%Furthermore, under certain choice of parameters, we can simplify  
More precisely, we have the following lemma.
Later on, we combine the following lemma with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.

\begin{lemma}
In the isotropic model, for some constant $c_0>0$, suppose that
\be\label{choiceofpara}
	\frac{pd^2}{\sigma^2} \le \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0}.
\ee
Then we have
\begin{align}
\te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }  \label{simple1}
\end{align}
w.h.p. for some constant $\e>0$.
\end{lemma}

\begin{proof}
	Using Lemma \ref{largedeviation}, we obtain that $\val(v)= N_2\cdot h(v)  \left( 1+\OO(p^{-1/2+\e})\right)$.
	We define the function
	\begin{align}
		h(v) =& \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
		& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
		& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
	\end{align}
	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
	Hence the validation loss in \eqref{approxvalid} reduces to
	\be\label{boundv-w}
		g(v)=\left[N_2\cdot h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)
	\ee
	with high probability for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.

Let $\hat w$ the minimizer of $h(v)$. The proof consists of two steps.
\squishlist
	\item First, we show that $\hat{w}$ is close to $1$.
	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
\squishend
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result.

\begin{claim}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
There exists a constant $C>0$ such that
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{w.h.p.}\ee
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{claim}
\begin{proof}
To be consistent with the notation $\hat w$, we shall change the name of the argument to $w$ in the proof. First it is easy to observe that $h(w)< h(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$. We first consider the case $w\ge 1$. We write
\begin{align}
	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
Notice that
$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
\begin{align*}
h'(w) \ge &~  \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
 &+~ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
		&-~ 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
\end{align*}
where the matrix $\cal A$ is
\begin{align*}
\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
\end{align*}
Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
\begin{align*}
\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
\end{align*}
as long as
$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
Hence $h'(w)>0$ on $(w_1,\infty)$, i.e. $h(w)$ is strictly increasing for $w>w_1$. This gives $\hat w\le w_1$.

>>>>

For the isotropic model in Section \ref{sec_similarity}, we actually have an easier and sharper bound than Lemma \ref{thm_model_shift}. %as follows.
\begin{lemma}\label{prop_model_shift_tight}
		In the setting of Lemma \ref{thm_model_shift}, assume that $\Sigma_1 =\id$,
		$\beta_2$ is a random vector that has i.i.d. entries with mean $0$, variance $\kappa^2$ and finite moments up to any order, and $(\beta_1-\beta_2)$ is a random vector that is independent of $\beta_2$ and has i.i.d. entries with mean $0$, variance $d^2$ and finite moments up to any order. Denote
		$\Delta^\star_{\bias} := \bigbrace{(1 - \hat{v})^2 \kappa^2 + d^2} \bigtr{\Pi(\hat v)}$, where $\Pi$ was defined in \eqref{defnpihat}.	Then we have with high probability,
		\begin{align*}
			\te(\hat{\beta}_t^{\MTL}) \le \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \ge  (\al_+^2(\rho_1)+\oo(1))\cdot  \Delta^\star_{\bias} \ , \\
			\te(\hat{\beta}_t^{\MTL}) \ge \te(\hat{\beta}_t^{\STL})\quad \text{ when: }\ \  & \Delta_{\vari} \le (\al_-^2(\rho_1)-\oo(1))\cdot  \Delta^\star_{\bias}\ ,
		\end{align*}
		where $\Delta_{\vari}$ was defined in \eqref{Deltavarv}.
\end{lemma}

@@

For any fixed $v\in \R$, $\beta_1 - v\beta_2$ is a random vector with i.i.d. entries with mean $0$ and variance $(1-v)^2\kappa^2 + d^2$. Then using the concentration result, Lemma \ref{largedeviation}, we get that for any constant $\e>0$, 
\begin{align}
&\left|\delta_{\bias}(v)- [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
&=  \left|(\beta_1 - {v} \beta_2)^\top \cal K^\top \cal K (\beta_1 - {v} \beta_2) - [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K)\right| \nonumber\\
&\le p^\e [(1-v)^2\kappa^2 + d^2] \left\{\tr\left[(\cal K^\top \cal K)^2\right]\right\}^{1/2} \lesssim p^{1/2+\e} [(1-v)^2\kappa^2 + d^2] \quad \text{w.h.p.},\label{anotherbeta}
\end{align}
where $\delta_{\bias}(v)$ was defined in \eqref{revise_deltabias}, $\cal K$ was defined as $\cal K:=v\Sigma_2^{1/2}({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1} X_1^{\top}X_1$, and in the last step we used $\|\cal K\|=\OO(1)$ by \eqref{eq_isometric}. Now for $\tr (\cal K^\top \cal K)$, we rewrite it as
\begin{align*}
v^2 \tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}(X_1^\top X_1)^2 \right].
\end{align*}
Bounding $(X_1^\top X_1)^2=(Z_1^\top Z_1)^2$ using \eqref{eq_isometric}, we obtain that
\be\label{anotherwtbeta} \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  [(1-v)^2\kappa^2 + d^2]\tr (\cal K^\top \cal K) \le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})),\ee
where
$$\delta^\star_{\bias}(v):=n_1^2 v^2 [(1-v)^2\kappa^2 + d^2]\tr \left[ ({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\Sigma_2({v}^2 X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}\right].$$
Note that $\delta^\star_{\bias}(v) \sim p$ by \eqref{eq_isometric}. Hence combining \eqref{anotherbeta} and \eqref{anotherwtbeta} we get
\be\label{replaceest}
  \delta^\star_{\bias}(v) \cdot (\al_-^2(\rho_1)-\OO(p^{-1/2+\e})) \le  \delta_{\bias}(v)\le \delta^\star_{\bias}(v) \cdot  (\al_+^2(\rho_1)+\OO(p^{-1/2+\e})).
\ee
Now we can replace the estimate \eqref{bounddelta-} with this stronger estimate, and repeat all the other parts of the proof of Lemma \ref{thm_model_shift} to conclude Lemma \ref{prop_model_shift_tight}. In particular, one can calculate $  \delta^\star_{\bias}(v)$ using Lemma \ref{lem_cov_derivative} and get the $  \Delta^\star_{\bias}(v)$ term. 
\end{proof}

We show that for the isotropic model, the optimum of $\hat v$ is very close to 1.
This allows us to simplify the expression of $\te(\hat{\beta}_2^{\MTL})$ significantly.
%Our main observation is that the optimum of $\val(v)$ is approximately $1$.This allows us to simplify the bias and variance bounds significantly.
%Furthermore, under certain choice of parameters, we can simplify  
More precisely, we have the following lemma.
Later on, we will combine it with Lemma \ref{prop_model_shift_tight} together to analyze the bias-variance tradeoff.

\begin{lemma}
In the isotropic model, suppose for some constant $c_0>0$, 
\be\label{choiceofpara}
	\frac{pd^2}{\sigma^2} = \OO(1),\quad p^{-1+c_0} \le \frac{\kappa^2}{\sigma^2 }  \le p^{-\e_0-c_0},
\ee
where $\e_0$ is the constant as appeared in \eqref{approxvalid}. Then we have
\begin{align}
\te(\hat{\beta}_2^{\MTL})=&(1+\OO(n^{-\e}))\cdot d^2 \tr\left[(X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber \\
&+(1+\OO(n^{-\e}))\cdot \sigma^2  \bigtr{(X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} } \quad \text{w.h.p.} \label{simple1}
\end{align}
for some constant $\e>0$.
\end{lemma}

\begin{proof}
	Using Lemma \ref{largedeviation} again, we can simplify \eqref{revise_eq_val_mtl} as $\val(v)= N_2h(v) \cdot  \left( 1+\OO(p^{-1/2+\e})\right)$, where the function $ h$ is defined as
	%We define the function
	\begin{align}
		h(v) =& \frac{\rho_1}{\rho_2}\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
		& +  v^2\left[d^2 +\left( v-1\right)^2\kappa^2\right]\cdot \tr\left[( v^2X_1^{\top}X_1 +X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
		& + \left(\frac{\rho_1}{\rho_2} v^2 + 1\right)\sigma^2 \cdot \bigtr{(v^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }. \nonumber
	\end{align}
	%\cor Under the setting of Lemma \ref{prop_model_shift_tight},
	Furthermore, the validation loss in \eqref{approxvalid} reduces to
	\be\label{boundv-w}
		g(v)=\left[N_2 h(v) + (N_1\sigma^2_1+N_2\sigma^2_2)\right]\cdot \left( 1+\OO(p^{-(1-\e_0)/2+\e})\right)\quad \text{w.h.p.}
	\ee
	for any constant $\e>0$. %\nc Thus for the following discussions, it suffices to focus on the behavior of $h (v)$.
Let $\hat w$ be the minimizer of $h(v)$. Our proof consists of the following two steps.
\squishlist
	\item First, we show that $\hat{w}$ is close to $1$.
	\item Second, with \eqref{boundv-w} we show that $\hat v$ is close to $\hat w$. Then we plug $\hat{v}$ into $\te(\hat{\beta}_2^{\MTL})$ to get \eqref{simple1}.
\squishend
%For the minimizer $\hat w$ of $\val(w)$, we have a similar result as in Proposition \ref{thm_cov_shift}.
For the first step, we will prove the following result.
\begin{claim}\label{lem_hat_v}
%Suppose the assumptions of Lemma \ref{prop_model_shift_tight} hold. Assume that $ \kappa^2 \sim pd^2 \sim \sigma^2$ are of the same order.
There exists a constant $C>0$ such that
	\be\label{hatw_add1}|\hat w -1|\le C\left(\frac{d^2}{\kappa^2} + \frac{\sigma^2}{p\kappa^2}\right)\quad \text{w.h.p.}\ee
	%is $\hat{w} = 1 \pm \bigo{\frac 1 {n_1+n_2}}$ \todo{(figure out the constants)}
\end{claim}
\begin{proof}
To be consistent with the notation $\hat w$, we change the name of the argument to $w$ in the proof. First it is easy to observe that $h(w)< h(-w)$ for $w> 0$. Hence it suffices to assume that $w\ge 0$. We first consider the case $w\ge 1$. We write
\begin{align}
	h(w) =&  \frac{\rho_1}{\rho_2}\left[\frac{d^2}{w^4} +\frac{\left( w-1\right)^2}{w^4}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right] \nonumber \\
	& + \left[\frac{d^2}{w^2} +\frac{\left( w-1\right)^2}{w^2}\kappa^2\right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
			& +  \frac{\rho_1}{\rho_2}\sigma^2  \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }+ \sigma^2 \cdot \bigtr{(w^2X_1^{\top}X_1  + X_2^{\top}X_2)^{-1} }.\nonumber%+  \sigma^2n_2 \cdot \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }. \nonumber
\end{align}
Notice that
$$\tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_i^{\top}X_i)^2\right],\ \ i=1,2, \quad \text{and} \quad \bigtr{(X_1^{\top}X_1  + w^{-2}X_2^{\top}X_2)^{-1} }$$
are increasing functions in $w$. Hence taking derivative of $h(w)$ with respect to $w$, we obtain that
\begin{align*}
h'(w) \ge & \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right] \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_2^{\top}X_2)^2\right]   \\
 &+ \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]\cdot \tr\left[( X_1^{\top}X_1 +w^{-2}X_2^{\top}X_2)^{-2} (X_1^{\top}X_1)^2\right] \nonumber\\
		&- 2  \frac{\sigma^2}{w^3} \cdot \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} X_1^\top X_1  } =  \bigtr{(X_1^{\top}X_1 + w^{-2}X_2^{\top}X_2)^{-2} \cal A },
\end{align*}
where the matrix $\cal A$ is defined as
\begin{align*}
\cal A :&= \frac{\rho_1}{\rho_2}\left[ \frac{2(w-1)(2-w)}{w^5}\kappa^2 - \frac{4d^2}{w^5}\right](X_2^{\top}X_2)^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right](X_1^{\top}X_1)^2 - 2 \frac{\sigma^2}{w^3}X_1^\top X_1.
\end{align*}
Using the estimate \eqref{eq_isometric}, we get that $\cal A$ is lower bounded as
\begin{align*}
\cal A \succeq&~ - \frac{4d^2}{w^5}n_1n_2 (\al_+(\rho_2)+\oo(1))^2 + \left[\frac{2\left( w-1\right)}{w^3}\kappa^2 - \frac{2d^2}{w^3} \right]n_1^2 (\al_-(\rho_1)-\oo(1))^2 \\
&~ - 2 \frac{\sigma^2}{w^3}n_1(\al_{+}(\rho_1)+\oo(1)) \succ 0,
\end{align*}
as long as
$$w> w_1:=1 +\frac{d^2}{\kappa^2}+ \frac{\sigma^2}{n_1\kappa^2}\frac{\al_{+}(\rho_1)+\oo(1)}{\al_{-}^2(\rho_1)} + \frac{2d^2}{\kappa^2}\frac{\rho_2(\al_+^2(\rho_2)+\oo(1))}{\rho_1\al_-^2(\rho_1) }.$$
Hence $h'(w)>0$ on $(w_1,\infty)$, i.e. $h(w)$ is strictly increasing for $w>w_1$. This gives $\hat w\le w_1$.
